Compositional equivalences based on Open pNets

### 2020-01-31 2016-Weak-FH-Bisim/WeakBisim.tex
note page 12 (re)

\paragraph{Note on finite versus infinite open automata:} as
mentionned in page \pageref{def:open-automaton}, we have defined two flavors of
automata. More precisely, in \cite{hou:hal-02406098}, we formely define
\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
and \emph{structural open automata} (finite) that can be generated as
the semantics of pNets (see Def. \ref{def:operationalSemantics}), and used in the implementation. Then we define
an alternative version of our bisimulation, called
structural-FH-Bisimulation, based on structural open automata, and
prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
In the sequel, all mentions of finite automata, and algorithms for
bisimulations, implicitely refer to their \emph{structural} versions.

If we assume that everything is finite (states and transitions in the
open automata, and the predicates in $\mathcal{R}$, then it is easy to
prove that it is decidable whether a relation is a 
FH-bisimulation, provided the logic of the predicates is
decidable (see \cite{henrio:Forte2016}). Formaly:

>>>>

\paragraph{Note on finite versus infinite open automata:} as
mentionned in page \pageref{def:open-automaton}, we have defined two flavors of
automata. More precisely, in \cite{hou:hal-02406098}, we formely define
\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
and \emph{structural open automata} (finite) that can be generated as
the semantics of pNets (see Definition \ref{def:operationalSemantics}), and used in the implementation. Then we define
an alternative version of our bisimulation, called
structural-FH-Bisimulation, based on structural open automata, and
prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
In the sequel, all mentions of finite automata, and algorithms for
bisimulations, implicitely refer to their \emph{structural} versions.

If we assume that everything is finite (states and transitions in the
open automata, and the predicates in $\mathcal{R}$, then it is easy to
prove that it is decidable whether a relation is a 
FH-bisimulation, provided the logic of the predicates is
decidable (proof in \cite{henrio:Forte2016}). Formaly:
